Title

### 2019-05-22 4_method.tex
explain end-of-markings better

\subsection{1. Compute MAT}

@@

\subsection{2. Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
Equivalently we can look at the angle $\alpha$ between a skeletal point and the two closest points on the outline.
(Same definition as \cite{attali1996modeling}.)
A computationally efficient way to compute the same can be obtained by looking at the ratio between $R$ and Euclidean distance.

\paragraph{line-line bones}
When the angle between two outline segments is small, the naive method will produce long triangular gaps.
Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.

@@

\paragraph{line-point bones}
\hl{reformulate in terms of $\alpha$}
For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
The angle between the outline segments is twice the angle between the MAT segment and an outline segment.
The angle between the MAT parabola and the x-axis is the inverse tangent of the derivative of this formula: $\tan^{-1} \left( \abs x / d \right)$.
The angle is less than \SI{60}{\degree} when 
$\tan^{-1} \left( \abs x / d \right) < \SI{30}{\degree}$ 
i.e. when $\abs x/d < 1 / \sqrt{3}$
i.e. when $\abs x < d / \sqrt{3}$.
So we mark the part of the parabola as to-be-transformed for which $x \in [-d / \sqrt{3}, d / \sqrt{3}]$.

>>>>

\subsection{Compute MAT}

@@

\subsection{Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
Equivalently we can look at the \emph{bisector angle} $\alpha$ between a skeletal point and the two closest points on the outline.
(Same definition as \cite{attali1996modeling}.)

\paragraph{line-line bones}
When the angle between two outline segments is small, the naive method will produce long triangular gaps.
A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between $R$ and Euclidean distance.
Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.

@@

\paragraph{line-point segments}
For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
If $\alpha > \SI{120}{\degree}$ then $\tan^{-1} \abs \partial y / \partial x < \SI{30}{\degree}$,
i.e.  $\tan^{-1} \abs x/d < \SI{30}{\degree}$,
i.e. when $\abs x/d < 1 / \sqrt{3}$,
i.e. when $\abs x < d \sqrt{3} / 3$.
So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.

\begin{figure}[H]
\centering
\includegraphics[width=.5\columnwidth]{sources/method/end_of_markings_point_line.pdf}
\caption{End-of-markings for a parabolic spine segment.}
\label{end_of_markings_point_point}
\end{figure}
